\subsection*{Publications}
\subsubsection*{Articles}
\begin{etaremune}
  \item Lisciandra, Chiara and Johannes Korbmacher. Forthcoming. ``Multiple Models, One Explanation.'' \emph{Journal of Economic Methodology}
  \item Anglberger, Albert and Johannes Korbmacher. 2019. ``Truthmakers and Normative Conflicts.'' \emph{Studia Logica}. Online First. \url{https://doi.org/10.1007/s11225-019-09862-5}.
  \item Alama, Jesse and Johannes Korbmacher. 2018. ``The Lambda Calculus.'' In: \emph{The Stanford Encyclopedia of Philosophy}, Summer 2018 Edition, edited by Edward N. Zalta, \url{https://plato.stanford.edu/archives/sum2018/entries/lambda-calculus/}.
  \item \footnote{This paper was included in the list of the most popular philosophy articles published by Oxford University Press in 2018 (\emph{Best of Philosophy}), \url{https://academic.oup.com/journals/pages/best_of_philosophy}.}Korbmacher, Johannes and Georg Schiemer. 2018. ``What Are Structural Properties?'' \emph{Philosophia Mathematica} 28(3): 295--323, \url{https://doi.org/10.1093/philmat/nkx011}
  \item Korbmacher, Johannes. 2018. ``Axiomatic Theories of Partial Ground I: The Base Theory.'' \emph{Journal of Philosophical Logic} 47(2): 161--91, \url{https://doi.org/10.1007/s10992-016-9423-9}
  \item Korbmacher, Johannes. 2018. ``Axiomatic Theories of Partial Ground II: Partial Ground and Typed Truth.'' \emph{Journal of Philosophical Logic} 47(2): 193--226,
  \item Anglberger, Albert, Johannes Korbmacher, and Federico Faroldi. 2016. ``An Exact Truthmaker Semantics for Explicit Permission and Obligation.'' In \emph{Deontic Logic and Normative Systems. 13th International Conference, DEON 2016, Bayreuth, Germany, July 18-21, 2016}, edited by Olivier Roy, Allard Tamminga, and, Malte Willer, 16--31. London, UK: College Publications, \url{https://tinyurl.com/yy27l4nn}.
  \item \footnote{This paper won the \emph{Best Paper Award} at the SoPhiA graduate conference 2015 at the University of Salzburg.}Korbmacher, Johannes. 2015. ``Yet Another Puzzle of Ground.'' \emph{Kriterion. A Journal of Philosophy} 29(2): 1--10, \url{https://tinyurl.com/yy523dst}
  \item Korbmacher, Johannes, Martin Pleitz, and Julia Schmidt. 2014. ``Dynamisierte Feldtheorie.'' In \emph{Freie Subjekte in der Welt der Physik. Die analytische Transzendentalphilosophie von Peter Rohs in der Diskussion}, edited by Attila Karaku\c{s}, Martin Pleitz, and Christian Weidemann, 133--56. M\"unster: Mentis.
  \item Korbmacher, Johannes, Markus Pohlmann, Sebastian Schmoranzer, and Ansgar Seide. 2010. ``Searle on External Realism.'' In \emph{John R.\ Searle. Thinking About the Real World}, edited by Dirk Franken, Attila Karakus, and Jan G.\ Michel, 133--42. Frankfurt: Ontos.
  \item Korbmacher, Johannes, Sebastian Schmoranzer, and Ansgar Seide. 2009. ``Simply False? Swinburne on Simplicity as Evidence of Truth.'' In \emph{Richard Swinburne. Christian Philosophy in a Modern World}, edited by Nicola M\"o\ss ner, Sebastian Schmoranzer, and Christian Weideman, 47--60. Frankfurt: Ontos.
\end{etaremune}
\subsubsection*{Other (Professional publications, etc.)}
\begin{etaremune}
  \item Column on Truthmaker Semantics for \emph{Whats Hot in Mathematical Philosophy?} 2019. In \emph{The Reasoner} 13(4), \url{https://tinyurl.com/y46xzjke}.
  \item Contributing author (10 lemmas), \emph{W\"orterbuch zur Sprach- und Kommunikationswissenschaft (WSK)}, de Gruyter, \url{https://www.degruyter.com/view/db/wsk}.
\end{etaremune} \vspace{1ex}
\begin{tabular}{l} See \url{https://research.jkorbmacher.org/papers} for Preprints and Drafts.
\end{tabular}
\subsection*{Talks}
\begin{etaremune}
  \item ``The Logic of Free Choice Permission'' (with Albert Anglberger). At: \emph{LIRa}, ILLC, University of Amsterdam (15/11/2018).
  \item ``The Logic of Free Choice Permission'' (with Albert Anglberger). At: \emph{OZSW 2018}, University of Twente (10/11/2018).
  \item ``Tableaux for the Logic of Exact Entailment.'' At: \emph{GAP.10}, University of Cologne (17--20/09/2018).
  \item ``The Logic of Free Choice Permission'' (with Albert Angelberger). At: \emph{GAP.10}, University of Cologne (17--20/09/2018).
  \item ``Elusive Knowledge Hyperintensionalized'' (with Janneke van Lith). At: \emph{GAP.10}, University of Cologne (17--20/09/2018).
  \item ``Tableaux for Exact Entailment.'' At: \emph{Amsterdam Metaphysics Seminar}, University of Amstedam (28/03/2018). Slides: \url{http://jkorbmacher.org/wp-content/uploads/2018/03/slides_tableaux.pdf}
  \item ``Tableaux for Exact Entailment.'' At: \emph{The Logic and Metaphysics of Ground}, University of Glasgow (15/03/2018).
  \item ``Truthmakers and Normative Conflicts'' (with Albert Anglberger). At: \emph{Hyperintensional Logics and Truthmaker Semantics}, University of Ghent (15/12/2017).
  \item ``Tableaux for the Logic of Exact Entailment.'' At: \emph{Hyperintensional Logics and Truthmaker Semantics}, University of Ghent (15/12/2017).
  \item ``Ex Pluribus Unum: How Many Models Support One Hypothesis'' (with Chiara Lisciandra). At: TP-Colloquium, Utrecht University (21/11/2017).
  \item ``Truth-Maker Bayesianism. Theory and Applications.'' At: \emph{OZSW 2017}, Utrecht University (10/11/2017).
  \item ``Ex Pluribus Unum: How Many Models Support One Hypothesis'' (with Chiara Lisciandra). At: EPSA 2017, University of Exeter (09/09/2017).
  \item ``Structural and Logical Properties'' At: SILFS 2017, University of Bologna (21/06/2017).
  \item ``Truth-Maker Bayesianism.'' At: Munich Center for Mathematical Philosophy (11/05/2017).
  \item ``An Exact Truthmaker Semantics for Explicit Permission and Obligation'' (with Albert Anglberger and Federico Faroldi) At: DEON 2016 (18/07/2016).
  \item ``An Exact Truthmaker Semantics for Explicit Permission and Obligation'' (with Albert Anglberger) At: Tilburg University (04/04/2016).
  \item ``Exact Truthmaker Semantics for Propositional Modal Logic(s)'' At: \emph{GroLog}, University of Groningen (31/03/2016).
  \item ``Truthmakers and Mathematics'' At: \emph{The Metaphysical `Because' and the Foundations of Mathematics}, University of Hamburg (22/01/2016).
  \item ``Hyperintensional Deontic Logic'' (with Albert Anglberger) At: University of Beyreuth (15/12/2015).
  \item ``Hyperintensional Deontic Logic'' (with Albert Anglberger) At: Deontic Logic and Ethics, Venice (26/11/2015).
  \item ``Toward Axiomatic Theories of Ground'' At: \emph{Logical and Metaphysical Perspectives on Grounding}, University of Osnabr\"uck (18/09/2015).
  \item ``How to Distinguish Necessarily Coextensive but Distinct Properties'' At: \emph{GAP.9}, University of Osnabr\"uck (15/09/2014).
  \item ``Yet Another Puzzle of Ground'' At: \emph{SoPhiA}, University of Salzburg (04/09/2015).
  \item ``What Are Structural Properties?'' At: \emph{Congress of Logic, Methodology and Philosophy of Science. Affiliated Session: Mathematical Objectivity by Representation}, University of Helsinki (03/08/2015).
  \item ``Mathematical Explanations and Nomological Ground'' (with Lorenzo Casini) At: \emph{Explanation Beyond Causation}, MCMP Munich (23--24/10/2014).
  \item ``On the Semantics of (Iterated) Ground'' At: \emph{Phloxshop VI --- Logics and (their) Grounds}, University of Hamburg (09/09/2014).
  \item ``What Are Structural Properties?'' (with Georg Schiemer) At: \emph{Symposium on the Foundations of Mathematics}, Kurt G\"odel Research Center, Vienna (08/07/2014).
  \item ``What Are Structural Properties?'' (with Georg Schiemer) At: \emph{Philosophy of Mathematics. Objectivity, Cognition and Proof}, Universit\`a Vita-Salute San Raffaele, Milan (05/29/2014).
  \item ``Proof Theory for the Propositional Logic of Ground.'' At: \emph{Groundedness in Semantics and Beyond}, University of Oslo (23/08/2013).
  \item ``Mathematical Metaphysics.' At: \emph{Workshop on Mathematical Philosophy}, SOPhiA 2013, Salzburg (12/09/2013).
  \item ``Sequent Calculus for the Logic of Ground.'' At: \emph{1st MCMP Munich -- Buenos Aires Workshop}, MCMP Munich (12/07/2013).
  \item ``Essence and Identity. A Note on Essential Properties and Criteria of Identity'' At: \emph{GAP.8}, University of Konstanz (19/09/2012).
  \item ``Ante--rem Structuralism and the Ontological Argument'' At: \emph{Structure and Identity Conference}, University of Bristol (24/07/2010).
  \item ``Das Benacerraf-Dilemma in der Philosophie der Mathematik'' At: \emph{Interdisziplin\"arer Arbeitskreis Logik, Argumentation, Wissenschaftstheorie}, University of Siegen (01/12/2009).
\end{etaremune}

\subsection*{Workshops and Conferences}
\begin{tabular}{l p{.8\linewidth}}
  \emph{24--29/08/2020} & \emph{European Congress of Analytic Philosophy (ECAP) 10} (congress, local organizing committee)\\[1ex]
  \emph{23--24/11/2018} & \emph{Exploring Hyperintensional Semantics} (workshop, co-organized with Janneke van Lith and Bj{\o}rn Jespersen)\\[1ex]
  \emph{18/09/2015} & \emph{Logical and Metaphysical Perspectives on Grounding} (workshop, co-organized with Jan Plate and Norbert Gratzl)\\
\end{tabular}

\subsection*{Services to the Profession}
\begin{tabular}{p{\linewidth}}
  Referee for
  \emph{Analysis},
  \emph{Cambridge University Press},
  \emph{Dialectica},
  \emph{The European Journal for the Philosophy of Science},
  \emph{Erkenntnis},
  \emph{FNRS - Fond de la Recherche Scientifique} (Franco-Belgian National Science Fond),
  \emph{The Journal of Philosophical Logic},
  \emph{Kriterion},
  \emph{Linguistics and Philosophy},
  \emph{The Logic Journal of the IGPL},
  \emph{Philosopher's Imprint},
  \emph{Philosophical Quarterly},
  \emph{The Review of Symbolic Logic},
  \emph{Studia Logica},
  \emph{Synthese},
  and the \emph{Swiss National Science Foundation}.

\end{tabular}

\subsection*{Professional Memberships}
\begin{tabular}{p{\linewidth}}
  \emph{Gesellschaft f\"ur analytische Philosophie (GAP)}, \emph{Nederlandse Onderzoekschool Wijsbegeerte (OZSW)}, \emph{Deutsche Gesellschaft f\"ur Philosophie (DGPhil)}\\
\end{tabular}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../cv.tex"
%%% End:
